---
title: "List of Korean Name Syllables"
author: "Xavier Marquez"
date: "6 July 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache= TRUE, cache.rebuild = TRUE)
```

The list of Korean name components is derived from the tables in https://en.wikipedia.org/wiki/List_of_Korean_given_names and https://en.wikipedia.org/wiki/List_of_Korean_family_names, plus a small number of syllables that are missing in these but are found in the KCNA headlines.

```{r read_data}
library(dplyr)
library(stringr)
library(rvest)

korean_given_names <- read_html("https://en.wikipedia.org/wiki/List_of_Korean_given_names") %>%
  html_table()

korean_family_names <- read_html("https://en.wikipedia.org/wiki/List_of_Korean_family_names") %>%
  html_table() %>%
  .[[1]] %>% select(-Hangul,-Hanja)

```

The tables need a lot of cleaning up. First we do the family names:

```{r clean_up_family_name}
library(tidyr)

names(korean_family_names)[4] <- "est_distribution"

korean_family_names <- reshape2::melt(korean_family_names,id.var="est_distribution") %>%
  transform(value = str_split(value, "[,.\\n]")) %>%
  unnest(value) %>% 
  filter(value != "") %>%
  mutate(value = str_replace_all(value," \\(.+\\).*$",""), value = str_trim(value, side = "both"))

knitr::kable(korean_family_names)
```

Now we clean up the given names. First the first syllable:

```{r clean_up_given_name}

library(purrr)
library(reshape2)
library(tidyr)

normal_korean_names <- korean_given_names[c(1:6)] %>% 
  map_df(.f = melt,id.vars = NULL, na.rm=TRUE, .id = "table") %>% 
  filter(value !="", value != " ") %>% 
  select(-variable) %>% 
  separate_rows(value, sep ="/") %>%
  separate(value, into = c("first_syllable","second_syllable")) 

normal_korean_names %>%
  knitr::kable()

first_syllable <- unique(normal_korean_names$first_syllable)

second_syllable <- unique(normal_korean_names$second_syllable)

first_syllable <- c(first_syllable,korean_given_names[[8]][,1],str_trim(korean_given_names[[8]][,3]),str_trim(korean_given_names[[8]][,4]))

first_syllable <- unique(first_syllable)

first_syllable <- c(first_syllable,unique(str_replace(korean_given_names[[9]][,1],"-.+$","")),unique(str_replace(korean_given_names[[9]][,3],"-.+$","")),unique(str_replace(korean_given_names[[9]][,4],"-.+$","")))

first_syllable <- unique(first_syllable)

first_syllable <- c(first_syllable,unique(str_replace(korean_given_names[[10]][,1],"-.+$","")),unique(str_replace(korean_given_names[[10]][,3],"-.+$","")),unique(str_replace(korean_given_names[[10]][,4],"-.+$","")))

first_syllable <- unique(first_syllable)

first_syllable <- c(first_syllable,unique(str_replace(korean_given_names[[11]][,1],"-.+$","")),unique(str_replace(korean_given_names[[11]][,3],"-.+$","")),unique(str_replace(korean_given_names[[11]][,4],"-.+$","")))

first_syllable <- unique(first_syllable)

first_syllable <- stringr::str_conv(first_syllable,"UTF-8")

first_syllable <- stringr::str_replace_all(first_syllable, " \\(.+$", "")



```

Then the second syllable:

```{r second_syllable_extraction}

second_syllable <- c(second_syllable,unique(str_replace(korean_given_names[[9]][,1],"^.+-","")),unique(str_replace(korean_given_names[[9]][,3],"^.+-","")),unique(str_replace(korean_given_names[[9]][,3],"^.+-","")))

second_syllable <- unique(second_syllable)

second_syllable <- c(second_syllable,unique(str_replace(korean_given_names[[10]][,1],"^.+-","")),unique(str_replace(korean_given_names[[10]][,3],"^.+-","")),unique(str_replace(korean_given_names[[10]][,4],"^.+-","")))

second_syllable <- unique(second_syllable)

second_syllable <- str_to_title(second_syllable)

second_syllable <- stringr::str_conv(second_syllable,"UTF-8")

first_syllable <- unique(c(first_syllable,second_syllable))

sort(first_syllable)

second_syllable <- unique(c(first_syllable,second_syllable))

sort(second_syllable)
```

Then we add some extras from a list of trigrams:

```{r add_from_trigrams}

trigrams2 <- readr::read_csv("./trigrams.csv")

family_name <- str_to_lower(korean_family_names  %>% .$value)

first_syllable <- str_to_lower(first_syllable)

second_syllable <- str_to_lower(second_syllable)

family_name <- c(family_name,trigrams2 %>% filter(!(V1 %in% family_name)) %>% .$V1 %>% unique())

first_syllable <- c(first_syllable,trigrams2 %>% filter(!(V2 %in% first_syllable)) %>% .$V2 %>% unique())

first_syllable <- c(first_syllable,c("si","pan","un","pong","ok","son", "gyun", "sa", "po", "am", "mong", "kon", "wang","to","moo", "san", "sat", "yon", "kwon", "bul"))

second_syllable <- c(second_syllable,trigrams2 %>% filter(!(V3 %in% second_syllable)) %>% .$V3 %>% unique())

second_syllable <- c("san","son","on", "gyon", "gyun", "po", "am", "mong", "kon", "wang", "an", "hon", "ma", "yon", "sin", "jak", "gat", "muk", "bong", "sin", second_syllable)

second_syllable <- second_syllable[ !grepl("grees|thanh",second_syllable) ]

sort(family_name)

sort(first_syllable)

sort(second_syllable)

korean_names <- list(family_name = family_name, first_syllable = first_syllable, second_syllable = second_syllable)

```

We check that it captures enough people:

```{r mentions_of_koreans, dependson=-1}

library(tidytext)

corpus_tokens <- unnest_tokens(KCNA::preprocessed_corpus %>% distinct(title), 
                               output = words, 
                               input = title, 
                               drop=FALSE, token = "regex", 
                               pattern = "[[:punct:]\\s]", collapse = FALSE)


corpus_tokens <- corpus_tokens %>%
  group_by(title) %>%
  mutate(words_2 = lead(words), words_3 = lead(words_2)) %>%
  ungroup()

mentioned <- corpus_tokens %>%
  select(words, words_2,words_3, title) %>%
  filter(words %in% korean_names$family_name,
         words_2 %in% c(korean_names$first_syllable), 
         words_3 %in% c(korean_names$second_syllable),
         str_detect(title,str_to_title(paste(words,words_2,words_3)))) %>%
  distinct(words,words_2,words_3) %>%
  mutate(mentioned = str_to_title(paste(words,words_2,words_3)))

nrow(mentioned)

knitr::kable(head(mentioned))

corpus_tokens <- left_join(corpus_tokens,mentioned)

corpus_mentions <- corpus_tokens %>%
  filter(!is.na(mentioned)) %>%
  distinct(title,mentioned)

preprocessed_corpus <- left_join(KCNA::preprocessed_corpus %>% select(-mentions_korean, -mentioned), corpus_mentions) %>%
  mutate(mentions_korean = !is.na(mentioned))

word_data <- preprocessed_corpus %>%
  mutate(old_title = title, title = str_to_lower(title))

mentioned <- mentioned %>%
  mutate(change_to = str_replace_all(mentioned," ", "_"))

word_data$title <- qdap::mgsub(paste0("\\b",str_to_lower(mentioned$mentioned),"\\b"),
                               mentioned$change_to,
                               word_data$title,
                               fixed = FALSE, ignore.case = TRUE, perl=TRUE)

word_data %>% 
  filter(grepl("_",title)) %>%
  sample_n(10) %>%
  distinct(date, title, old_title) %>%
  knitr::kable()

word_data %>%
  filter(grepl("[A-Z][a-z]{1,3} [A-Z][a-z]{1,3} [A-Z][a-z]{1,3}\\b",old_title), !mentions_korean) %>%
  distinct(title,old_title) %>%
  knitr::kable()
```

And we check that it captures only people:

```{r captures_people, dependson=-1}

word_data %>%
  filter(grepl("_",title)) %>%
  group_by(mentioned) %>%
  summarise(sample_title = sample(title,1), total = n()) %>%
  ungroup() %>%
  arrange(desc(total)) %>%
  knitr::kable()

```

Finally we create a list and save:

```{r save_data}

devtools::use_data(korean_names,overwrite=TRUE)

```

